---
title: "LR2_Example"
author: "Anthony Stachowitz"
date: "June 4, 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Point to local file repository:

Set the local directory for this project.


```{r}
setwd("C:\\Users\\Anthony\\Desktop\\R studio projects\\LR2-exercise")
```

### Load the National Health Interview Survey data:

load dataset NatHealth2011.rds into NH11 and set labs to NH11$label attributes.

```{r}
NH11 <- readRDS("dataSets/NatHealth2011.rds")
labs <- attributes(NH11)$labels
```

###   predict the probability of being diagnosed with hypertension based on age, sex, sleep, and bmi:

#### check structure of hypev.
```{r}
str(NH11$hypev)
```

#### check levels of hypev.
```{r}
levels(NH11$hypev)
```

#### collapse all missing values to NA.
```{r}
NH11$hypev <- factor(NH11$hypev, levels=c("2 No", "1 Yes"))
```

#### run our regression model.
```{r}
hyp.out <- glm(hypev~age_p+sex+sleep+bmi,
              data=NH11, family="binomial")
coef(summary(hyp.out))
```

#### transform the coefficients to make them easier to interpret.
```{r}
hyp.out.tab <- coef(summary(hyp.out))
hyp.out.tab[, "Estimate"] <- exp(coef(hyp.out))
hyp.out.tab
```

### How much more likely is a 63 year old female to have hypertension compared to a 33 year old female?

#### Create a dataset with predictors set at desired levels.
```{r}
predDat <- with(NH11,
                expand.grid(age_p = c(33, 63),
                            sex = "2 Female",
                            bmi = mean(bmi, na.rm = TRUE),
                            sleep = mean(sleep, na.rm = TRUE)))
```

#### predict hypertension at those levels
```{r}
cbind(predDat, predict(hyp.out, type = "response",
                       se.fit = TRUE, interval="confidence",
                       newdata = predDat))
```

#### use the effects package to compute quantities of interest for us (cf. the Zelig package).
```{r, echo=FALSE, message=FALSE}
library(effects)
```
```{r}
plot(allEffects(hyp.out))
```

## Exercise: logistic regression

###   1. Use glm to conduct a logistic regression to predict ever worked
###      (everwrk) using age (age_p) and marital status (r_maritl).
###   2. Predict the probability of working for each level of marital
###      status.

###   Predict the probability of working for each level of marital status:

#### check structure of everwrk.
```{r}
str(NH11$everwrk)
```

#### check levels of everwrk.
```{r}
levels(NH11$everwrk)
```

#### collapse all missing values to NA.
```{r}
NH11$everwrk <- factor(NH11$everwrk, levels=c("2 No", "1 Yes"))
```

#### Make marital status abbreviations for easier placement on the plot.
```{r}
levels(NH11$r_maritl) <- c("U 14","Marr_IH","Marr_OH", "Marr_UK", "Wid", "Div", "Sep", "Nev Mar", "LWP", "Unk")
```

#### run our regression model.
```{r}
wrk.out <- glm(everwrk~age_p+r_maritl,
              data=NH11, family="binomial")
coef(summary(wrk.out))
```

#### transform the coefficients to make them easier to interpret.
```{r}
wrk.out.tab <- coef(summary(wrk.out))
wrk.out.tab[, "Estimate"] <- exp(coef(wrk.out))
wrk.out.tab
```

### What is the probability of work at each marital level??

#### Create a dataset with predictors set at desired levels.
```{r}
predDat2 <- with(NH11,
                expand.grid(r_maritl = c("Marr_IH","Marr_OH", "Wid", "Div", "Sep", "Nev Mar", "LWP", "Unk"),
                            age_p = mean(age_p, na.rm = TRUE)))
```

#### predict if ever worked at those levels.
```{r}
cbind(predDat2, predict(wrk.out, type = "response",
                       se.fit = TRUE, interval="confidence",
                       newdata = predDat2))
```

#### use the effects package to compute quantities of interest for us (cf. the Zelig package).
```{r, echo=FALSE, message=FALSE}
library(effects)
```
```{r, fig.width=12, fig.height=7}
plot(allEffects(wrk.out))
```


